Efficient pedigree recording for fast population genetics simulation

### 2017-12-28 forwards_paper.tex
not on y-axis scales

\begin{figure}
    \includegraphics[]{sims/memuse}
    \caption{\label{sfig:ramsel}Peak RAM use in gigabytes (GB) for simulations with selection.  The plots are from the
        same data as in Figure \ref{fig:runtimes_selection}.}
\end{figure}

\begin{figure}
    \includegraphics[]{sims/memuse_nosel}
    \caption{\label{sfig:ramnosel}Peak RAM use in gigabytes (GB) for simulations without selection.  The plots are from
    the same data as in Figure \ref{sfig:rawspeed_nosel}.}
\end{figure}
\end{document}

>>>>

\begin{figure}
    \includegraphics[]{sims/memuse}
    \caption{\label{sfig:ramsel}Peak RAM use in gigabytes (GB) for simulations with selection.  The plots are from the
        same data as in Figure \ref{fig:runtimes_selection}. Note that the y-axis scales differ considerably across
    panels.}
\end{figure}

\begin{figure}
    \includegraphics[]{sims/memuse_nosel}
    \caption{\label{sfig:ramnosel}Peak RAM use in gigabytes (GB) for simulations without selection.  The plots are from
    the same data as in Figure \ref{sfig:rawspeed_nosel}. Note that the y-axis scales differ considerably across panels.}
\end{figure}
\end{document}
